---
title: "Activity3"
author: "Guillermo Romero"
date: "2022-08-04"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(skimr)
library(GGally)
```

```{r}
names(diamonds)
dim(diamonds)
summary(diamonds)
head(diamonds)
tail(diamonds)
skimr::skim(diamonds)
```

```{r, eval=FALSE}
ggpairs(diamonds) 
```

```{r}
ggplot(data = diamonds, aes(x = carat, y = price)) + geom_point()
```

```{r}
ggplot(data = diamonds, aes(x = carat)) + geom_histogram()
```

Create a new R Markdown document in your project, save as `r-exploring``
Attach the tidyverse, skimr, and GGally packages in the setup code chunk
Run View(diamonds) in the Console to look at the built-in diamonds dataset in R
Explore the dataset using the functions names(), dim(), summary(), head(), tail(), and skimr::skim()
Create a pairs plot using ggpairs()
Create a basic ggplot scatterplot of diamond price (price) as a function of size (carat)
Create a histogram showing the distribution of values in the carat column (recall: a histogram only requires a single variable, e.g. aes(x = carat))
Save, stage, commit, pull, then push your changes back to your repo in RStudio using the GUI interface (buttons)
Create a jitterplot (see: geom_jitter) of diamond clarity (on the x-axis) and price (y-axis).
Using git commands in the Terminal, stage, commit, & push changes
